---
title: "Children subset of Ten percent sample of 2021 Ghana Census data"
output: github_document
---

### History

-   **May 2025:**
    -   Downloaded the source data from the Ghana Statistical Service Microdata Catalog.
    -   url: <https://microdata.statsghana.gov.gh/index.php/catalog/110/get-microdata>
    -   The  original data was in the csv file format, size about 4 GB.

#### Load packages

```{r load r packages, eval = FALSE, include = TRUE}
library(arrow)
library(dplyr)
```

Using the `arrow` r package to load the data into the r environment. This package is helpful when working with large data sets.

```{r create arrow connection, eval = FALSE, include = TRUE}

phc_2021_sample <- arrow::open_dataset(
  sources = "~/path/to/data/defacto_population_20221011d.csv", 
  format = "csv"
 
)

```

#### Children subset

Due to errors saving the complete data set as a Parquet file, six columns and rows 1134 and 3050 were dropped.

-   Dropped Columns 137, 192, 204, 216, 218, 220

-   Creating a new data set `subset_gh_phc_201_ten_percent_sample` with 3,083,570 rows and 235 columns.

```{r children subset, eval = FALSE, include = TRUE}

subset_gh_phc_2021_ten_percent_sample <-
  phc_2021_sample[c(1:1133,1135:3049,3051:3083572),c(1:136,138:191,193:203,205:215,217, 219,221:241)]  |>
  dplyr::collect()
```

#### Write 3 million rows csv to parquet files

Partitioning by the variable `subdist` which represents the subdistricts of Ghana.

```{r write data set, eval = FALSE, include = TRUE}

arrow::write_dataset(dataset = subset_gh_phc_2021_ten_percent_sample,
                     partitioning = "subdist",
 
                    path = "~/Ama_Owusu-Darko_RCode_sample/rGhanaCensus/data/subset_gh_phc_2021_ten_percent_sample_parquet_file")

sessioninfo::session_info()

 
```
