---
title: "Create_interactive_map_displaying_Ghana_2019_School_Attendance_Indicators"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Create_interactive_map_displaying_Ghana_2019_School_Attendance_Indicators}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Load required packages

```{r setup}

library(rGhanaCensus)
library(sf)
library(tmap)
library(dplyr)
library(magrittr)
```

### Example 1

Create a interactive map with the package `tmap` and data from the package `rGhanaCensus` that displays the regional distribution of the *Percentage of students 3 years or older who have dropped out of school.*

Load geometry data G`hana_2021_school_attendance_geometry` from `rGhanaCensus` package.

```{r load_geometry_data, echo=TRUE}
data("Ghana_2021_school_attendance_geometry", package = "rGhanaCensus")
```

Convert it to `sf` data frame and assign a new name. In this example, "Ghana_edu_sf" will be the name of the `sf` data frame created.

```{r convert_to_sf_data_frame}
Ghana_edu_sf<- sf::st_as_sf(Ghana_2021_school_attendance_geometry)
```

The code `Ghana_edu_sf %>%filter(Locality=="Urban")` subsets the data frame and retains only the rows that the survey respondents came from Urban areas.

`Ghana_edu_sf %>%filter(Locality=="Rural")` can be used to retain observations from Rural areas.

```{r Example1}

#Use tmap to create interactive map
tmap_mode("view")

Ghana_edu_sf %>%
      dplyr::filter(Locality=="Urban") %>%
      tm_shape()+
      tm_polygons(id="Region", col="Percent_Dropped_out_of_School")+
      tm_text(text="Percent_Dropped_out_of_School")+
      tm_facets(by="Gender")
```

The code `tm_facets(by="Gender")` specifies facets (multiple maps) by Gender.

### Example 2

Create a interactive map with the package `tmap` and data from the package `rGhanaCensus` that displays *the regional distribution of population densities of students 3 years or older who have dropped out of school.*

```{r Example2}

#Load geometry data
data("Ghana_2021_school_attendance_geometry", package = "rGhanaCensus")

#Convert to sf data frame
Ghana_edu_sf<- sf::st_as_sf(Ghana_2021_school_attendance_geometry)

#Use tmap to create interactive map
tmap_mode("view")

Ghana_edu_sf %>%
      dplyr::filter(Locality=="Urban") %>%
      tm_shape()+
      tm_polygons(id="Region",col="Dropped_out_of_School", palette = "RdPu",
                  style="kmeans", convert2density = TRUE)+ tm_facets(by="Gender")
```

The `convert2density` argument in the `tm_polygon` function calculates the population density using the raw count values of the variable `Dropped_out_of_School` where the area size is in this case approximated from the shape object.
